Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-07 demystify.tex
updates

Some universities have \emph{research faculty} or research scientists, who are typically non-tenure line faculty who focus on research (e.g., publishing papers and getting grants). While they cannot solely graduate PhD students, they often co-advise and mentor students with tenure-line faculty. They can recruit students and provide RA funding for them.

>>>>

Some universities have \emph{research faculty} or research scientists, who are typically non-tenure line faculty and focus on research (e.g., publishing papers and getting grants). While they cannot solely graduate PhD students, they often co-advise and mentor students with tenure-line faculty. They can recruit students and provide RA funding for them.  They can also teach classes, but typically have a lower teaching load than teaching faculty.
